### 2016-11-07 paper1.tex
Added short captions for each figure

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/onestar_column.eps}
    \caption{Column density projections from the simulations of a single star
        cluster with mass $3\times10^4\;\mathrm{M_\odot}$, $50\;\mathrm{Myr}$
        after the cluster has formed.  The superbubble feedback model (center
        column) produces bubbles with radius and enclosed mass that match well
        to the direct injection simulations (left column).  This is shown
        quantitatively in figure~\ref{onestar_homogeneous} and
        figure~\ref{onestar_clumpy}.  The simple model (right column), despite
        injecting the same amount of energy, fails to generate enough hot mass
        inside the bubble, and subsequently suppresses the growth of Vishniac
        instabilities along the bubble edge because of the poorly resolved hot
        interior.}
    \label{onestar_column}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/onestar_homogeneous.eps}
    \caption{Feedback effects as a function of resolution.  The above figure
        shows on the left the total radial momentum imparted to the medium, and
        on the right the total amount of mass heated to above
        $10^5\;\mathrm{K}$.  The red curves are the direct injection results, the
        blue corresponds to the simple feedback, while the green shows the
        results of the superbubble model.  Solid lines show the values from
        simulations run with resolutions of $128^3$ particles, dashed for
    $64^3$, and dotted for $32^3$.
Note that for the $32^3$ run, the simple model produces $\sim 2\times
10^5\;M_\odot$ of hot gas.}
    \label{onestar_homogeneous}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_hottemp.eps}
    \caption{Peak temperature of feedback-heated gas inside the isolated star
        cluster's hot bubble.  Evaporation quickly enters the self-regulating
        regime, and the temperature is roughly constant for the last 
    $15\;\mathrm{Myr}$ of feedback.}
    \label{onestar_hottemp}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_kappa.eps}
    \caption{Hot mass production as a function of the conduction coefficient
        $\kappa_0$.  As this figure shows, reducing $\kappa_0$ by a factor of
        100 reduces the amount of hot mass generated through conduction by only
        a factor of $\sim2$. All $\kappa_0$ values have units of $\mathrm{erg\;
        s^{-1} K^{-7/2} cm^{-1}}$.}
    \label{onestar_kappa}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_clumpypoints.eps}
    \caption{3 kpc wide slices from the same three methods shown in
        figure~\ref{onestar_column}, also at 50 Myr, but applied to a star
        cluster in an inhomogeneous medium.  Particles whose smoothing length
        intersects z=0~kpc are shown.  Particles above $10^5$ K are shown in red.
        The upper row shows simulations with a single clump, while the bottom row
        shows simulations with 6 clumps.}
    \label{onestar_clumpyslice}
\end{figure}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/onestar_clumpy.eps}
    \caption{Feedback effects as a function of ISM homogeneity.  The above
        figure shows on the left the total radial momentum imparted to the
        medium, and on the right the total amount of mass heated to above
        $10^5\;\mathrm{K}$.  The red curves are the direct injection results, the
        blue corresponds to the simple feedback, while the green shows the
        results of the superbubble model.  Solid curves show the results for a
        homogeneous ISM, dashed for a single dense clump, and dotted for 6 dense
        clumps.}
    \label{onestar_clumpy}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/disc_phase.eps}
    \caption{Phase diagrams for the Milky Way (left) and dwarf (right)
        simulations at $200\;\mathrm{Myr}$.  The central panel shows a typical
        path for gas ejected from the Milky Way.  First gas cools radiatively
        (cyan path) to high density, where it becomes multiphase as its hot
        component is heated to $\sim10^7\;\mathrm{K}$ by feedback (red path)
        from nearby stars formed from its neighbouring high density gas.  The
        hot phase cools primarily through adiabatic expansion (green path).
        This process is often repeated one or more times, with gas that is
        entirely hot phase being ejected from the disc.  Cooling times of
        $10^4\;\mathrm{yr}$ and $10^6\;\mathrm{yr}$ are shown in blue. {\bf The
        majority of the hot gas in the upper left quadrant of the phase
        diagram has cooling times $>10^8\;\mathrm{yr}$.  The cooling curve
        for $10^8\;\mathrm{yr}$ passes through the green curve.}  Note that
        particles in the multiphase state show the temperature and density for
        each state as separate points.  The mean properties of multiphase particles
        would place them in regions with short cooling times.}
    \label{disc_phase}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_column.eps}
    \caption{Column Density (upper row) and temperature for the Milky Way
        simulation at $300\;\mathrm{Myr}$.  The vectors show the in-plane velocity.
        Temperatures shown are averages between the two phases for multiphase
        particles.  Black points in the face-on images show stars formed within
        the last $20\;\mathrm{Myr}$. Note that gas is both leaving the disc near the galactic
        core, and returning in some places near the edge.}
    \label{milkyway_column}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_outflow.eps}
    \caption{Outflow evolution for the Milky Way-like simulation.  The left
        hand plot shows the star formation rate and the outflow
        rate The right hand plot shows the average outflow
        velocity.}
    \label{milkyway_outflow}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/dwarf_column.eps}
    \caption{Column Density (upper row) and temperature for the dwarf simulation
        at $300\;\mathrm{Myr}$.  The vectors in show the in-plane velocity.  Temperatures
        shown are once again averages between the two phases for multiphase
        particles.  Note the much more `puffed up' appearance compared to the
        Milky Way, due to the more mass-loaded winds}
    \label{dwarf_column}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/dwarf_outflow.eps}
    \caption{Outflow evolution for the dwarf galaxy.  Note that the vertical
    ranges are different than in figure~\ref{milkyway_outflow}}
    \label{dwarf_outflow}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/kennicutt_schmidt.eps}
    \caption{Kennicutt-Schmidt law in the Milky Way-like (blue points) and dwarf
        (red triangles) galaxies at $500\;\mathrm{Myr}$. Surface densities were
        calculated in radial annuli.  The dashed line shows the
        Kennicutt-Schmidt Law.  The superbubble model is easily able to regulate
        star formation rates to within this range.}
    \label{kennicutt_schmidt}
\end{figure}

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/multiphase_properties.eps}
    \caption{Properties of multiphase particles in the galaxy simulations.  The
        top figure shows duration of multiphase state for particles in both
        galaxy simulations.  Particles that are in the multiphase state more
        than once (convert back to single phase, cool, and then receive feedback
        again) have each time they are multiphase counted separately. The bottom
        figure shows maximum heights reached by particles in the multiphase
        state.  For each particle that is ever in the multiphase state, the
    maximum height it reaches {\it while still multiphase} is shown above for
    both galaxy simulations.  Dashed lines show scale heights at
    $10^4\;\mathrm{K}$ for each
of the two simulations.}
    \label{multiphase_properties}
\end{figure}

>>>>

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/onestar_column.eps}
    \caption[Column density plot of a superbubble from a single cluster]{Column
    density projections from the simulations of a single star cluster with mass
    $3\times10^4\;\mathrm{M_\odot}$, $50\;\mathrm{Myr}$ after the cluster has
    formed.  The superbubble feedback model (center column) produces bubbles
    with radius and enclosed mass that match well to the direct injection
    simulations (left column).  This is shown quantitatively in
    figure~\ref{onestar_homogeneous} and figure~\ref{onestar_clumpy}.  The
    simple model (right column), despite injecting the same amount of energy,
    fails to generate enough hot mass inside the bubble, and subsequently
    suppresses the growth of Vishniac instabilities along the bubble edge
    because of the poorly resolved hot interior.}
    \label{onestar_column}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/onestar_homogeneous.eps}
    \caption[Feedback effects as a function of resolution]{Feedback effects as a
    function of resolution.  The above figure shows on the left the total radial
    momentum imparted to the medium, and on the right the total amount of mass
    heated to above $10^5\;\mathrm{K}$.  The red curves are the direct injection
    results, the blue corresponds to the simple feedback, while the green shows
    the results of the superbubble model.  Solid lines show the values from
    simulations run with resolutions of $128^3$ particles, dashed for $64^3$,
    and dotted for $32^3$.  Note that for the $32^3$ run, the simple model
    produces $\sim 2\times 10^5\;M_\odot$ of hot gas.}
    \label{onestar_homogeneous}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_hottemp.eps}
    \caption[Peak temperature of feedback-heated gas in a superbubble]{Peak
    temperature of feedback-heated gas inside the isolated star cluster's hot
    bubble.  Evaporation quickly enters the self-regulating regime, and the
    temperature is roughly constant for the last $15\;\mathrm{Myr}$ of
    feedback.}
    \label{onestar_hottemp}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_kappa.eps}
    \caption[Dependence of superbubble heated gas on conduction coefficient]{Hot
    mass production as a function of the conduction coefficient $\kappa_0$.  As
    this figure shows, reducing $\kappa_0$ by a factor of 100 reduces the amount
    of hot mass generated through conduction by only a factor of $\sim2$. All
    $\kappa_0$ values have units of $\mathrm{erg\; s^{-1} K^{-7/2} cm^{-1}}$.}
    \label{onestar_kappa}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/onestar_clumpypoints.eps}
    \caption[Image of superbubbles in a clumpy ISM]{3 kpc wide slices
    from the same three methods shown in figure~\ref{onestar_column}, also at 50
    Myr, but applied to a star cluster in an inhomogeneous medium.  Particles
    whose smoothing length intersects z=0~kpc are shown.  Particles above $10^5$
    K are shown in red.  The upper row shows simulations with a single clump,
    while the bottom row shows simulations with 6 clumps.}
    \label{onestar_clumpyslice}
\end{figure}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/onestar_clumpy.eps}
    \caption[Feedback effects as a function of ISM homogeneity]{Feedback effects
    as a function of ISM homogeneity.  The above figure shows on the left the
    total radial momentum imparted to the medium, and on the right the total
    amount of mass heated to above $10^5\;\mathrm{K}$.  The red curves are the
    direct injection results, the blue corresponds to the simple feedback, while
    the green shows the results of the superbubble model.  Solid curves show the
    results for a homogeneous ISM, dashed for a single dense clump, and dotted
    for 6 dense clumps.}
    \label{onestar_clumpy}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/disc_phase.eps}
    \caption[Phase diagram of gas in isolated galaxies]{Phase diagrams for the
    Milky Way (left) and dwarf (right) simulations at $200\;\mathrm{Myr}$.  The
    central panel shows a typical path for gas ejected from the Milky Way.
    First gas cools radiatively (cyan path) to high density, where it becomes
    multiphase as its hot component is heated to $\sim10^7\;\mathrm{K}$ by
    feedback (red path) from nearby stars formed from its neighbouring high
    density gas.  The hot phase cools primarily through adiabatic expansion
    (green path).  This process is often repeated one or more times, with gas
    that is entirely hot phase being ejected from the disc.  Cooling times of
    $10^4\;\mathrm{yr}$ and $10^6\;\mathrm{yr}$ are shown in blue. {\bf The
    majority of the hot gas in the upper left quadrant of the phase diagram has
    cooling times $>10^8\;\mathrm{yr}$.  The cooling curve for
    $10^8\;\mathrm{yr}$ passes through the green curve.}  Note that particles in
    the multiphase state show the temperature and density for each state as
    separate points.  The mean properties of multiphase particles would place
    them in regions with short cooling times.}
    \label{disc_phase}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_column.eps}
    \caption[Column density and temperature images of isolated Milky Way]{Column
    Density (upper row) and temperature for the Milky Way simulation at
    $300\;\mathrm{Myr}$.  The vectors show the in-plane velocity.  Temperatures
    shown are averages between the two phases for multiphase particles.  Black
    points in the face-on images show stars formed within the last
    $20\;\mathrm{Myr}$. Note that gas is both leaving the disc near the galactic
    core, and returning in some places near the edge.}
    \label{milkyway_column}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/milkyway_outflow.eps}
    \caption[Outflow evolution in isolated Milky Way]{Outflow evolution for the
    Milky Way-like simulation.  The left hand plot shows the star formation rate
    and the outflow rate The right hand plot shows the average outflow
    velocity.}
    \label{milkyway_outflow}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/dwarf_column.eps}
    \caption[Column density and temperature images of isolated dwarf]{Column
    Density (upper row) and temperature for the dwarf simulation at
    $300\;\mathrm{Myr}$.  The vectors in show the in-plane velocity.
    Temperatures shown are once again averages between the two phases for
    multiphase particles.  Note the much more `puffed up' appearance compared to
    the Milky Way, due to the more mass-loaded winds}
    \label{dwarf_column}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures1/dwarf_outflow.eps}
    \caption[Outflow evolution in isolated dwarf]{Outflow evolution for the
    dwarf galaxy.  Note that the vertical ranges are different than in
    figure~\ref{milkyway_outflow}}
    \label{dwarf_outflow}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/kennicutt_schmidt.eps}
    \caption[Kennicutt-Schmidt law for isolated galaxies]{Kennicutt-Schmidt law
    in the Milky Way-like (blue points) and dwarf (red triangles) galaxies at
    $500\;\mathrm{Myr}$. Surface densities were calculated in radial annuli.
    The dashed line shows the Kennicutt-Schmidt Law.  The superbubble model is
    easily able to regulate star formation rates to within this range.}
    \label{kennicutt_schmidt}
\end{figure}

\begin{figure}
    \includegraphics[width=0.5\textwidth]{figures1/multiphase_properties.eps}
    \caption[Properties of multiphase particles]{Properties of multiphase
    particles in the galaxy simulations.  The top figure shows duration of
    multiphase state for particles in both galaxy simulations.  Particles that
    are in the multiphase state more than once (convert back to single phase,
    cool, and then receive feedback again) have each time they are multiphase
    counted separately. The bottom figure shows maximum heights reached by
    particles in the multiphase state.  For each particle that is ever in the
    multiphase state, the maximum height it reaches {\it while still multiphase}
    is shown above for both galaxy simulations.  Dashed lines show scale heights
    at $10^4\;\mathrm{K}$ for each of the two simulations.}
    \label{multiphase_properties}
\end{figure}

### 2016-11-07 paper2.tex
Added short captions for each figure

    \caption{Mock stellar image of each galaxy at $z=0$.  The top row
    shows the galaxies edge-on, while the bottom shows them face-on.  The
    no-feedback case shows very little disc, while the blastwave feedback case has
    a thin disc with a prominent bulge.  The superbubble galaxy appears nearly
    bulgeless, composed only of a truncated disc. Note also that the superbubble
    galaxy is bluer than the blastwave or no-feedback galaxies, evidence of a
    younger stellar population.}

@@

    \caption{HI column density for the four test cases at z=0.  The no feedback case has
    exhausted nearly all of the gas within the disc, leaving only diffuse
    wisps.  The two superbubble cases (especially with doubled supernova energy)
    have lofted a large amount of gas out of the disc, and some entrained dense

@@

    \caption{Rotation curves for each of our test cases.  As is clear,
        the superbubble cases have much lower central concentrations, giving a
        a rotation curve that rises to a flat $200\; \rm{km/s}$.  The peaked rotation
        curves in the cases with blastwave or no feedback are a result of their
        failure to remove low angular momentum gas at high redshift, giving
        bulge-dominated, centrally concentrated galaxies.}

@@

    \caption{Histogram of stellar orbit circularity.  The bimodal distribution
        shows the bulge component, with a circularity near 0, and the disc
        component, with a circularity near 1.  Note that without feedback, this
        bimodality disappears, as the galaxy morphology becomes spheroidal.  The
        values here are normalized so that each curve has a total integral of
        unity.  As is clear, very few stars produced in a galaxy with superbubble
        feedback have low angular momentum, giving us a disc-dominated galaxy.}

@@

    \caption{Stellar mass growth as a function of the total halo mass.  The grey
    band and black dashed curve show mean values and uncertainties from the
    abundance matching results of \citet{Behroozi2013}.  The points show values at
    redshifts 3,2,1,0.5, and 0.1.  The stars show the final values at redshift 0.
    For essentially the entire evolution of the halo, both the no feedback galaxy
    and the blastwave galaxy overproduce stars.}

@@

    \caption{Stellar mass fraction as a function of time/redshift.  As in
    figure~\ref{mass_growth}, only the fiducial superbubble run produces stellar
    mass fractions within observed uncertainties for the entire history of the
    halo. The grey band is as in figure~\ref{mass_growth}, and here we also show, in
    the hatched region with the dotted curve, values and uncertainties from
    \citet{Moster2013}.  The dip that can be observed in the no feedback case
    at high redshift come from the growth of the halo, as it accretes dark
    matter dominated dwarves.}

@@

    \caption{Star formation rates for all 4 simulations.  The low star formation
    rate seen after $z=1$ in the no feedback case is due simply to the high z
    star formation consuming most of the available gas.}

@@

    \caption{Star formation rate up to $z=2$ for our superbubble galaxy.  As is
        clear, when sampled on short ($7\; \rm{Myr}$) timescales, the star
        formation rate in the superbubble galaxy is characterized by strong
        bursts, despite its quiescent behavior averaged over longer
    timescales.}

@@

    \caption{Galactic wind mass-loading and outflow rates for each feedback
    model.  As is clear, superbubble feedback powers winds with significantly
    higher mass-loadings, and, despite forming less than half as many stars the
    blastwave galaxy, results in more total outflowing gas.  This is key to the
    regulatory power of superbubbles.  Despite the peak in outflow rate in the 
    blastwave case between $z=4-1.5$, the massively increased star formation rate
    seen in the the smoothed SFR during this time (bottom plot) means that the
    mass-loadings never go above 5, and baryon expulsion is inefficient.}

@@

    \caption{Net baryonic accretion (stars and gas) for each test case.  It is
        clear that superbubble feedback expels baryons much more effectively
        than the blastwave feedback model (although even weak feedback does help
        somewhat compared to no feedback whatsoever).}

@@

    \caption{Inflow and outflow rates for superbubble (red) and blastwave
        (blue) run.  The solid lines show
        the total inflow rate, while the dashed and dotted lines show rates for
    cold and hot gas (above/below $10^5\; \rm{K}$) respectively.  }

@@

    \caption{In all four test cases, including the fiducial superbubble run
        shown above by the solid curve, and the no-feedback case shown by the
        dotted curve, the vast majority of low angular momentum material, with
        specific angular momentum $ j_z < 500\; \rm {kpc\; km/s}$, is accreted
        by $z=2$.  The accretion of high angular momentum material, with $j_z >
        1500\; \rm{kpc\; km/s}$ rises to peak at $z=2$, and continues to accrete
        $\sim 2\; \rm{M_\odot/yr}$ at $z=0$.  As can be seen here, the net flux
        of low angular momentum material at high redshift is suppressed, while
        the accretion of high angular momentum material at low redshift is
    actually {\it enhanced} by superbubble feedback.}

@@

    \caption{High-redshift winds preferentially remove low angular momentum
        material.  As can be seen here, significantly more low angular momentum
        material is removed by superbubble feedback than by the weaker
        blastwave feedback, but the amount of ejected high-angular
        momentum material is roughly equal.}

@@

    \caption{Phase diagram of gas in the halo at $z=0$.  The hot, coronal gas

>>>>

    \caption[Mock stellar image of galaxy at z=0 with different feedback
    models]{Mock stellar image of each galaxy at $z=0$.  The top row shows the
    galaxies edge-on, while the bottom shows them face-on.  The no-feedback case
    shows very little disc, while the blastwave feedback case has a thin disc
    with a prominent bulge.  The superbubble galaxy appears nearly bulgeless,
    composed only of a truncated disc. Note also that the superbubble galaxy is
    bluer than the blastwave or no-feedback galaxies, evidence of a younger
    stellar population.}

@@

    \caption[HI column density in a galaxy at z=0 with different feedback models]{HI
    column density for the four test cases at z=0.  The no feedback case has
    exhausted nearly all of the gas within the disc, leaving only diffuse wisps.
    The two superbubble cases (especially with doubled supernova energy) have
    lofted a large amount of gas out of the disc, and some entrained dense

@@

    \caption[Rotation curves with different feedback models]{Rotation curves for
    each of our test cases.  As is clear, the superbubble cases have much lower
    central concentrations, giving a a rotation curve that rises to a flat
    $200\; \rm{km/s}$.  The peaked rotation curves in the cases with blastwave
    or no feedback are a result of their failure to remove low angular momentum
    gas at high redshift, giving bulge-dominated, centrally concentrated
    galaxies.}

@@

    \caption[Stellar orbit circularity histogram]{Histogram
    of stellar orbit circularity.  The bimodal distribution shows the bulge
    component, with a circularity near 0, and the disc component, with a
    circularity near 1.  Note that without feedback, this bimodality disappears,
    as the galaxy morphology becomes spheroidal.  The values here are normalized
    so that each curve has a total integral of unity.  As is clear, very few
    stars produced in a galaxy with superbubble feedback have low angular
    momentum, giving us a disc-dominated galaxy.}

@@

    \caption[Stellar mass growth for different feedback models]{Stellar mass
    growth as a function of the total halo mass.  The grey band and black dashed
    curve show mean values and uncertainties from the abundance matching results
    of \citet{Behroozi2013}.  The points show values at redshifts 3,2,1,0.5, and
    0.1.  The stars show the final values at redshift 0.  For essentially the
    entire evolution of the halo, both the no feedback galaxy and the blastwave
    galaxy overproduce stars.}

@@

    \caption[Stellar mass fraction evolution]{Stellar mass fraction as a
    function of time/redshift.  As in figure~\ref{mass_growth}, only the
    fiducial superbubble run produces stellar mass fractions within observed
    uncertainties for the entire history of the halo. The grey band is as in
    figure~\ref{mass_growth}, and here we also show, in the hatched region with
    the dotted curve, values and uncertainties from \citet{Moster2013}.  The dip
    that can be observed in the no feedback case at high redshift come from the
    growth of the halo, as it accretes dark matter dominated dwarves.}

@@

    \caption[Star formation rate as a function of feedback model]{Star formation
    rates for all 4 simulations.  The low star formation rate seen after $z=1$
    in the no feedback case is due simply to the high z star formation consuming
    most of the available gas.}

@@

    \caption[Superbubble star formation burstiness]{Star formation rate up to
    $z=2$ for our superbubble galaxy.  As is clear, when sampled on short ($7\;
    \rm{Myr}$) timescales, the star formation rate in the superbubble galaxy is
    characterized by strong bursts, despite its quiescent behavior averaged over
    longer timescales.}

@@

    \caption[Galactic wind mass loading for different feedback models]{Galactic
    wind mass-loading and outflow rates for each feedback model.  As is clear,
    superbubble feedback powers winds with significantly higher mass-loadings,
    and, despite forming less than half as many stars the blastwave galaxy,
    results in more total outflowing gas.  This is key to the regulatory power
    of superbubbles.  Despite the peak in outflow rate in the blastwave case
    between $z=4-1.5$, the massively increased star formation rate seen in the
    the smoothed SFR during this time (bottom plot) means that the mass-loadings
    never go above 5, and baryon expulsion is inefficient.}

@@

    \caption[Net baryonic accretion for different feedback models]{Net baryonic
    accretion (stars and gas) for each test case.  It is clear that superbubble
    feedback expels baryons much more effectively than the blastwave feedback
    model (although even weak feedback does help somewhat compared to no
    feedback whatsoever).}

@@

    \caption[Inflow and outflow rates for different feedback models]{Inflow and
    outflow rates for superbubble (red) and blastwave (blue) run.  The solid
    lines show the total inflow rate, while the dashed and dotted lines show
    rates for cold and hot gas (above/below $10^5\; \rm{K}$) respectively.  }

@@

    \caption[Net accretion as a function of angular momentum]{In all four test
    cases, including the fiducial superbubble run shown above by the solid
    curve, and the no-feedback case shown by the dotted curve, the vast majority
    of low angular momentum material, with specific angular momentum $ j_z <
    500\; \rm {kpc\; km/s}$, is accreted by $z=2$.  The accretion of high
    angular momentum material, with $j_z > 1500\; \rm{kpc\; km/s}$ rises to peak
    at $z=2$, and continues to accrete $\sim 2\; \rm{M_\odot/yr}$ at $z=0$.  As
    can be seen here, the net flux of low angular momentum material at high
    redshift is suppressed, while the accretion of high angular momentum
    material at low redshift is actually {\it enhanced} by superbubble
    feedback.}

@@

    \caption[High redshift winds remove low angular momentum gas]{High-redshift
    winds preferentially remove low angular momentum material.  As can be seen
    here, significantly more low angular momentum material is removed by
    superbubble feedback than by the weaker blastwave feedback, but the amount
    of ejected high-angular momentum material is roughly equal.}

@@

    \caption[Gas phase diagram for g1536]{Phase diagram of gas in the halo at $z=0$.  The hot, coronal gas
